---
title: "2021 German federal election manifestos"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE)
```

Repository containing manifestos of the main parties competing in the 2021 German federal elections (26 September 2021). The repository currently contains the manifesto versions listed below.

Party | Description
--|--
AfD | [Final version](https://cdn.afd.tools/wp-content/uploads/sites/111/2021/05/2021-05-20-_-AfD-Bundestagswahlprogramm-2021.pdf)
CDU/CSU | [Final version](https://www.csu.de/common/download/Regierungsprogramm.pdf)
FDP | [Final version](https://www.fdp.de/sites/default/files/2021-06/FDP_Programm_Bundestagswahl2021_1.pdf)
Greens | [Final version](https://www.gruene.de/artikel/wahlprogramm-zur-bundestagswahl-2021)
The Left | [Final version](https://www.die-linke.de/fileadmin/download/wahlen2021/BTWP21_Entwurf_Vorsitzende.pdf)
SPD | [Final version](https://www.spd.de/fileadmin/Dokumente/Beschluesse/Programm/SPD-Zukunftsprogramm.pdf)


## Files

The repository contains the manifestos in the following formats:

- **Original PDF files**: the folder `manifestos_originals` contains the manifestos published on the parties' websites
- **Edited PDF files**: the folder `manifestos_clean_pdf` contains cleaned PDF files. I removed title pages, page numbers, headers, footers, table of contents, and the index
- **Text files**: the folder `manifestos_clean_txt` contains `.txt` files of the cleaned PDFs
- **Corpus**: the file `data_corpus_manifestos_ger2021.rds` contains all party manifestos as a [**quanteda**](https://quanteda.io) text corpus. The corpus object also includes meta data on each variables, including the party codes for the [ParlGov](http://www.parlgov.org) and the [Manifesto Project](https://manifesto-project.wzb.eu) datasets.

**Note**: I [manually checked the txt files for errors](https://github.com/stefan-mueller/data_manifestos_ger2021/commit/852923fb96c2393689fb1ccbc2ed15312517d67a) resulting from hyphenation in the original documents. Yet, the txt files may still contain errors. Please check the raw texts carefully before you use them for your own research Feel free to push a clean and updated file to this repository.

## Example

This example shows how to load the corpus object and extract the most frequent terms in each manifesto (with minimal pre-processing and no compounding of multiword expressions).


```{r,message=FALSE}
## Load packages
library(quanteda)
library(quanteda.textstats)
library(ggplot2)

## Load text corpus
data_corpus_manifestos_ger2021 <- readRDS("data_corpus_manifestos_ger2021.rds")

## Get summary of corpus
textstat_summary(data_corpus_manifestos_ger2021)

## Tokenize corpus and transform to document-feature matrix
dfmat_man <- data_corpus_manifestos_ger2021 %>% 
  tokens(remove_punct = TRUE, remove_numbers = TRUE) %>% 
  tokens_compound(phrase("* innen")) %>%  # compound *innen
  tokens_remove(pattern = c(stopwords("de"), "dass")) %>% 
  dfm()


## Get most frequent words by party
tstat_freq <- textstat_frequency(dfmat_man, 
                                 groups = party_name_short, 
                                 n = 10)

## Plot most frequent words
ggplot(data = tstat_freq, aes(x = factor(nrow(tstat_freq):1), y = frequency)) +
  geom_point() +
  facet_wrap(~group, scales = "free_y") +
  coord_flip() +
  scale_x_discrete(breaks = nrow(tstat_freq):1,
                   labels = tstat_freq$feature) +
  labs(x = NULL, y = "Most frequent words") +
  theme_minimal()
```


## Citation

Feel free to use the manifestos or edited files for your own work. Please cite the data as follows:

Stefan Müller. 2021. _2021 German federal election manifestos_. Version 0.2: https://github.com/stefan-mueller/data_manifestos_ger2021.

If you have any questions or suggestions, please file a [GitHub issue](https://github.com/stefan-mueller/data_manifestos_ger2021/issues) or [get in touch with me](https://muellerestefan.net).
